%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Full Name}{}
\email{xxxxx@gmail.com}
\phone[mobile]{+91 1234567890}               
\address{Village, City - State, Country}


\begin{document}

\recipient{To}{The Teacher-In-Charge, \\
               Department of Computer Application,\\ 
               Full Address (State)}
\date{\today}
\opening{\textbf{Sub: Application for the post of Guest Lecturer (Computer Application) with reference advertisement: XXXX/XX, dated 04-03-2022.}}
\closing{Your Sincerly, \vspace{-1em}}


\enclosure[Enclosed (Marksheets/Certificates)]{
              \\ 1. SSLC (Admit/MarkSheet/Certificate)
                 \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
                 2. Diploma (MarkSheet/Certificate)
                 \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\        
                 3. B.Tech (MarkSheet/Certificate)
                 \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
                 4. M.Tech (MarkSheet/Certificate)
                 \hspace{2.1em} 8. Caste Certificate \\
                 }
\makelettertitle


Dear Hiring Manager,

\vspace{1em}
I am writing to express my strong interest in the opportunity at your company. With my extensive background in Artificial Intelligence and Machine Learning, I am confident that I possess the skills and experience necessary to make significant contributions to your team.

\vspace{1em}
My academic foundation in AI Engineering from MIT, coupled with my practical experience as a Software Engineer at Microsoft, has equipped me with a deep understanding of the latest advancements in the field. My proficiency in Machine Learning, developed through both theoretical study and hands-on projects, allows me to effectively design, implement, and optimize AI solutions.

\vspace{1em}
During my time at Microsoft, I focused on developing and deploying AI/ML models for various applications, gaining valuable insights into the challenges and opportunities within the industry. I am eager to leverage my technical expertise and problem-solving skills to contribute to your company's success.

\vspace{1em}
I am a highly motivated and results-oriented individual with a strong work ethic and a passion for pushing the boundaries of AI technology. I am confident that I can quickly adapt to your company's culture and make a positive impact from day one.

\vspace{1em}
Thank you for your time and consideration. I am available for an interview at your earliest convenience.

\vspace{1em}
Sincerely,

\vspace{1em}
Daniel Stevens 
ds@example.com 



\end{document}